Bandit Multiclass Linear Classification: Efficient Algorithms for the Separable Case

### 2019-01-22 ICML-submission/introduction.tex
Fix typos in introduction

The bandit feedback setting, however, is much more challenging. For the case
when the examples are strongly linearly separable, to the best of our knowledge,
it is not known how to design an efficient algorithm with a finite mistake bound
before our work.~\footnote{Although~\cite{Chen-Chen-Zhang-Chen-Zhang-2009}
claimed that their Conservative OVA algorithm with PA-I update has a finite
mistake bound under the strong linear separability condition, their proof of
Theorem 2 is incorrect: first, their Theorem 2 implies a mistake upper bound of
$\frac{R}{\gamma}$ with sufficiently large $C$, which contradicts our lower
bound in Theorem~\ref{theorem:strongly-separable-examples-mistake-lower-bound};
second, their Lemma 4 cannot be directly applied to the bandit setting, as the
algorithm only makes updates on a subset of the $w_i$'s.} We design a simple and
efficient algorithm
(Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples})
that makes at most $O(K (R/\gamma)^2))$ mistakes in expectation. Its memory
complexity and per-round time complexity are both $O(dK)$. The algorithm can be
viewed as running $K$ copies of the \textsc{Binary Perceptron} algorithm, one
copy for each class. We prove that any (possibly randomized) algorithm must make
$\Omega(K (R/\gamma)^2))$ mistakes in the worst case. The extra $O(K)$
multiplicative factor in the mistake bound, as compared to the full-information
setting, is the price we pay for the bandit feedback, or more precisely, the
lack of full-information feedback.

For the case when the examples are weakly linearly separable, it was open for a
long time whether there exist \textit{efficient} algorithms with finite mistake
bound~\cite{Kakade-Shalev-Shwartz-Tewari-2008, Beygelzimer-Orabona-Zhang-2017}.
Furthermore, in~\cite{Kakade-Shalev-Shwartz-Tewari-2008}, they ask the question:
Is there \textit{any} algorithm with a finite mistake bound that has no explicit
dependence on the dimensionality of the feature vectors? We answer both
questions affirmatively by providing an efficient algorithm with finite
dimensionless mistake bound (Algorithm~\ref{algorithm:kernelized}).\footnote{An
in inefficient algorithm was given by~\cite{Daniely-Helbertal-2013}.}

The strategy used in Algorithm~\ref{algorithm:kernelized} is to construct a
non-linear feature mapping $\phi$ and associated positive definite kernel
$k(x,x')$ that makes the examples \emph{strongly} linearly separable in a
higher-dimensional space. We then use the kernelized version of
Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} for
the strongly separable case (Algorithm~\ref{algorithm:kernelized}). The kernel
$k(x,x')$ corresponding to the feature mapping $\phi$ has a simple explicit
formula and can be computed in $O(d)$ time, making
Algorithm~\ref{algorithm:kernelized} computationally efficient. For details on
kernel methods see e.g.~\citet{Scholkopf-Smola-2002} or
\citet{Shawe-Taylor-Cristianini-2004}.

>>>>

The bandit feedback setting, however, is much more challenging. For the case
when the examples are strongly linearly separable, to the best of our knowledge,
it is not known how to design an efficient algorithm with a finite mistake bound
before our work.~\footnote{Although~\cite{Chen-Chen-Zhang-Chen-Zhang-2009}
claimed that their Conservative OVA algorithm with PA-I update has a finite
mistake bound under the strong linear separability condition, their proof of
Theorem 2 is incorrect: first, their Theorem 2 implies a mistake upper bound of
$\frac{R}{\gamma}$ with sufficiently large $C$, which contradicts our lower
bound in Theorem~\ref{theorem:strongly-separable-examples-mistake-lower-bound};
second, their Lemma 4 cannot be directly applied to the bandit setting, as the
algorithm only makes updates on a subset of the $w_i$'s.} We design a simple and
efficient algorithm
(Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples})
that makes at most $O(K (R/\gamma)^2)$ mistakes in expectation. Its memory
complexity and per-round time complexity are both $O(dK)$. The algorithm can be
viewed as running $K$ copies of the \textsc{Binary Perceptron} algorithm, one
copy for each class. We prove that any (possibly randomized) algorithm must make
$\Omega(K (R/\gamma)^2)$ mistakes in the worst case. The extra $O(K)$
multiplicative factor in the mistake bound, as compared to the full-information
setting, is the price we pay for the bandit feedback, or more precisely, the
lack of full-information feedback.

For the case when the examples are weakly linearly separable, it was open for a
long time whether there exist \textit{efficient} algorithms with finite mistake
bound~\cite{Kakade-Shalev-Shwartz-Tewari-2008, Beygelzimer-Orabona-Zhang-2017}.
Furthermore, \citet{Kakade-Shalev-Shwartz-Tewari-2008} ask the question:
Is there \textit{any} algorithm with a finite mistake bound that has no explicit
dependence on the dimensionality of the feature vectors? We answer both
questions affirmatively by providing an efficient algorithm with finite
dimensionless mistake bound (Algorithm~\ref{algorithm:kernelized}).\footnote{An
in inefficient algorithm was given by~\cite{Daniely-Helbertal-2013}.}

The strategy used in Algorithm~\ref{algorithm:kernelized} is to construct a
non-linear feature mapping $\phi$ and associated positive definite kernel
$k(x,x')$ that makes the examples \emph{strongly} linearly separable in a
higher-dimensional space. We then use the kernelized version of
Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} for
the strongly separable case. The kernel $k(x,x')$ corresponding to the feature
mapping $\phi$ has a simple explicit formula and can be computed in $O(d)$ time,
making Algorithm~\ref{algorithm:kernelized} computationally efficient. For
details on kernel methods see e.g.~\citet{Scholkopf-Smola-2002} or
\citet{Shawe-Taylor-Cristianini-2004}.
